Impact of grids and dynamical cores in CESM2.2 on the surface mass balance of the Greenland Ice Sheet

### 2022-05-05 arcticgrids.tex
mods

While the summer cloud forcing biases are consistent with the summer temperature biases in Figure~\ref{fig:dThyps} -- regions where clouds are too reflective coincide with regions that are too cold -- it is not clear whether the cold biases are caused by the cloud biases, or whether the cold biases amplify the cloud forcing bias. ({\color{blue}{This ends abruptly. Anything else to add?}} {\color{purple}{Causation I agree is hard to prove due to energy transport, but in summer cloud fraction is probably playing a role. The likely other thing that could be playing a role is surface albedo (absorbed solar). Could note that.}})

@@

The ice sheet interior receives too little shortwave radiation in the coarser grids. On the VR grids, both the interior shortwave deficit and the excessive shortwave around the ocean perimeter are improved. This suggests that the coarse-grid clouds are too thick in the Greenland interior and too thin around the perimeter. This is consistent with the total summer cloud fraction bias, computed from the CALIPSO cloud dataset and shown in the top panel of Figure~\ref{fig:FSDS}. Note that total cloud fraction characterizes the cloud field at all vertical levels, and attenuates the changes arising from any single layer due to the occurrence of overlapping clouds at all other levels. Despite the attenuated signal, the cloud fractions are too high in the interior and and too low around the oceanic perimeter, in the coarser grids, while the VR grids have an overall reduction in total cloud fraction bias.

@@

The more accurate representation of orographic precipitation on the higher resolution grids is consistent with the cloud and radiation biases, cf. Figures~\ref{fig:SWCF}, \ref{fig:FSDS}, and \ref{fig:prect}. The agreement of the cloud and precipitation biases in and around Greenland from multiple independent datasets indicates that the biases are a robust feature of the coarser grids. The reduced biases on the VR grids suggest that the biases in the coarse models are a result of insufficient horizontal resolution.

>>>>

The summer cloud forcing biases are consistent with the summer temperature biases in Figure~\ref{fig:dThyps} -- regions where clouds are too reflective coincide with regions that are too cold. While we have not quantified the role of the clouds in contributing to the cooler Arctic temperatures, shortwave radiation is a crucial component of the Arctic energy budget during summer. The shortwave cloud forcing biases are on the order of 10 W/m2, which is a significant fraction of the total absorbed shortwave during Arctic summer  \cite{SETAL2007JGR} and is therefore likely a factor contributing to the cooler temperatures.

@@

The ice sheet interior receives too little shortwave radiation in the coarser grids. On the VR grids, both the interior shortwave deficit and the excessive shortwave around the ocean perimeter are improved. This suggests that the coarse-grid clouds are too thick in the Greenland interior and too thin around the perimeter. This is consistent with the total summer cloud fraction bias, computed from the CALIPSO cloud dataset and shown in the top panel of Figure~\ref{fig:FSDS}. Note that total cloud fraction characterizes the cloud field at all vertical levels, and attenuates the changes arising from any single layer due to the occurrence of overlapping clouds at other levels. Despite the attenuated signal, the cloud fractions are too high in the interior and and too low around the oceanic perimeter in the coarser grids, whereas the VR grids have an overall improvement in total cloud fraction bias.

@@

The more accurate representation of orographic precipitation in the VR grids is consistent with the cloud and radiation biases, cf. Figures~\ref{fig:SWCF}, \ref{fig:FSDS}, and \ref{fig:prect}. The agreement of the cloud and precipitation biases in and around Greenland from multiple independent datasets indicates that the biases are a robust feature of the coarser grids. The reduced biases on the VR grids suggest that the biases in the coarse models are a result of insufficient horizontal resolution.
